Handbook streamFind: Backend

### 2023-03-07 README.Rmd
Updated README and cleaning

The R package [streamFind](https://github.com/ricardobachertdacunha/streamFind) (this repository) is the back-end platform for the streamFind project entitled "Flexible data analysis and workflow designer to identify chemicals in the water cycle". The streamFind project is funded by the [Bundesministerium für Bildung und Forschung (BMBF)](https://www.bmbf.de) and is a cooperation between the [Institut für Energie- und Umwelttechnik e. V. (IUTA)](https://www.iuta.de) and [Forschungszentrum Informatik (FZI)](https://www.fzi.de/). The major focus of streamFind is data processing for environmental and quality studies. The streamFind aims to stimulate the use of advanced data analysis (e.g., non-target screening, statistical analysis, etc.) in routine studies, promoting standardization of data processing and structure and easing the retrospective evaluation of data. The streamFind package can be used by academics but also by technicians due to the comprehensive documentation and well categorized set of integrated functions or modules (see vignettes for more information).

@@

[R](https://cran.r-project.org/) and [RTools](https://cran.r-project.org/bin/windows/Rtools/) for Windows users. The `r R.version.string` can be obtained in https://cran.r-project.org/. The RTools can be downloaded in https://cran.r-project.org/bin/windows/Rtools/. Make sure to download the right version for the R version installed. Installation instructions are given in both sources.

The patRoon's [handbook](https://rickhelmus.github.io/patRoon/handbook_bd/manual-installation.html#r-prerequisites) offers detailed information on how to install the [patRoon](https://github.com/rickhelmus/patRoon) R package and the required [dependencies](https://rickhelmus.github.io/patRoon/handbook_bd/manual-installation.html#other-dependencies).

@@

The [streamFind](https://github.com/ricardobachertdacunha/streamFind) R package can be installed from the GitHub repository with the following code line.

@@

The [streamFindData](https://github.com/ricardobachertdacunha/streamFindData) R package holds the data used in examples and other documentation assets of the streamFind R package and can be installed from the GitHub repository with the following code line.

>>>>

The R package [streamFind](https://github.com/ricardobachertdacunha/streamFind) (this repository) is the back-end framework for the streamFind project entitled "Flexible data analysis and workflow designer to identify chemicals in the water cycle". The streamFind project is funded by the [Bundesministerium für Bildung und Forschung (BMBF)](https://www.bmbf.de) and is a cooperation between the [Institut für Energie- und Umwelttechnik e. V. (IUTA)](https://www.iuta.de) and [Forschungszentrum Informatik (FZI)](https://www.fzi.de/). The major focus of streamFind is data processing for environmental and quality studies. The streamFind aims to stimulate the use of advanced data analysis (e.g., non-target screening, statistical analysis, etc.) in routine studies, promoting standardization of data processing and structure and easing the retrospective evaluation of data. The streamFind package can be used by academics but also by technicians due to the comprehensive documentation and well categorized set of integrated functions or modules (see vignettes for more information).

@@

[R](https://cran.r-project.org/) and [RTools](https://cran.r-project.org/bin/windows/Rtools/) (the latter is only recommended for Windows users). The [handbook](https://rickhelmus.github.io/patRoon/handbook_bd/manual-installation.html#r-prerequisites) of the [patRoon](https://github.com/rickhelmus/patRoon) R package offers detailed installation instructions, including the required [dependencies](https://rickhelmus.github.io/patRoon/handbook_bd/manual-installation.html#other-dependencies).

@@

The [streamFind](https://github.com/ricardobachertdacunha/streamFind) R package can be installed from the GitHub repository.

@@

The [streamFindData](https://github.com/ricardobachertdacunha/streamFindData) R package holds the data used in examples and other documentation assets of the streamFind R package and can be installed from the GitHub repository.
